Phenotype pleiotropy of regulatory variants increases with the variety of bound transcription factors, regulated genes and active tissues

### 2022-08-27 ms/ms05_floats.tex
ENH ms

% full size table is table*
\begin{table*}[]
\centering
\scriptsize
\hline
\csvreader[separator=tab,
tabular=rrrrcp{0.6\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Pos. (hg38) & \bfseries Variant & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_rsid_most_pleiotropic.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv & \csvcolvi}% specify your coloumns here
\hline
%
\vspace{15pt}
%
  \caption{Colocalized eQTL/GWAS variants involved in 5 or more GWAS categories. Genomic coordinates are given for the hg38 assembly. }\label{tab:pleitropic_variants}
\end{table*}

@@

\begin{figure*}[]
\centering
%
\begin{subfigure}[]{.66\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_3.png}
\end{subfigure}

@@

\begin{figure*}[]
\centering
%
\begin{subfigure}[]{.66\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_tissue_enrich_in_pleio.py/plt.png}
\end{subfigure}
%
\caption{Tissue category odds ratio in pleitropic variants compared with variant with GWAS category count 1.} \label{fig:geneontology}
\end{figure*}

@@

% full size table is table*
\begin{table*}[H]
\centering
\scriptsize
\hline
\csvreader[
separator=tab,
tabular=rrrrcp{0.5\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Start (hg38) & \bfseries End (hg38) & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_region_window_100000_pleio_highest.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv & \csvcolvi}% specify your coloumns here
\hline
%
\vspace{15pt}
\caption{Pleiotropic regions involving 5 or more GWAS categories. Genomic coordinates are given for the hg38 assembly.}\label{tab:pleiotropic_regions}
\end{table*}

@@

\begin{figure*}[]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/regions_100000_length_hist.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
\end{subfigure}
%
\caption{Analysis of pleiotropic regions. \textbf{a}, Length distribution of pleiotropic regions. \textbf{b}, Cumulative sum ordered inversely with the number of GWAS categories.} \label{fig:pleiotropy_region_distribution}
\end{figure*}

@@

\begin{figure*}[]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
\end{subfigure}
%
\caption{Percentage of colocalized eQTL/GWAS variants with different number of GWAS categories (\textbf{a}), egenes (\textbf{b}) and etissues (\textbf{c}).} \label{fig:hist_gwas_egene_etissue}
\end{figure*}

@@

\begin{figure*}[!ht]

\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

\begin{subfigure}[]{.33\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{e}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{f}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

\begin{subfigure}[]{.33\textwidth}
\textbf{g}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{h}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{i}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/missense_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/splice_region_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/3_prime_UTR_variant.png}
%
\end{subfigure}
%
\caption{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: \textbf{a}, Missense variant, \textbf{b}, splice region variant and \textbf{c}, 3' UTR variant.} \label{fig:vep_consequence}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{Count of egenes per variant-tissue (\textbf{a}), etissues per variant-egene (\textbf{b}) and GWAS categories per variant-egene-etissue (\textbf{c}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remaptf.py/bxplt_remaptf_per_rsid_flank_0.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_remap_crm_gwas_categories.py/remap_crm_fisher.png}
\end{subfigure}
%
\caption{Analysis of transcription factor binding. \textbf{a}, Binding count of transcription factors in the region surrounding pleiotropic variants (Radius 50 bp) as a function of the GWAS category count. \textbf{b}, Odds ratio of cis regulatory module-annotated vs non-annotated variants.} \label{fig:freq_tf_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_beta.py/eqtl_beta.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_beta.py/gwas_beta.png}
\end{subfigure}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{\textwidth}

>>>>

% full size table is table*
\begin{table*}[!tbp]
\centering
\scriptsize
\hline
\csvreader[separator=tab,
tabular=ccrrp{0.4\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Pos (hg38) & \bfseries Variant & \bfseries GWAS Categories\\\hline,
]{fig/tab_rsid_most_pleiotropic.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolvi}% specify your coloumns here
\hline
%
\vspace{15pt}
%
  \caption{Colocalized eQTL/GWAS variants involved in 5 or more GWAS categories. Genomic coordinates are given for the hg38 assembly. }\label{tab:pleitropic_variants}
\end{table*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.66\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_davidgo.py/david_pleio_3.png}
\end{subfigure}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.66\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_tissue_enrich_in_pleio.py/plt.png}
\end{subfigure}
%
\caption{Tissue category odds ratio in pleitropic variants compared with variant with GWAS category count 1.} \label{fig:geneontology}
\end{figure*}

@@

% full size table is table*
\begin{table*}[!tbp]
\centering
\scriptsize
\hline
\csvreader[
separator=tab,
tabular=ccrrp{0.45\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Start & \bfseries End & \bfseries GWAS Categories\\\hline,
]{fig/tab_region_window_100000_pleio_highest.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolvi}% specify your coloumns here
\hline
%
\vspace{15pt}
\caption{Pleiotropic regions involving 5 or more GWAS categories. Genomic coordinates are given for the hg38 assembly.}\label{tab:pleiotropic_regions}
\end{table*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/regions_100000_length_hist.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
\end{subfigure}
%
\caption{Analysis of pleiotropic regions. \textbf{a}, Length distribution of pleiotropic regions. \textbf{b}, Cumulative sum ordered inversely with the number of GWAS categories.} \label{fig:pleiotropy_region_distribution}
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
\end{subfigure}
%
\caption{Percentage of colocalized eQTL/GWAS variants with different number of GWAS categories (\textbf{a}), egenes (\textbf{b}) and etissues (\textbf{c}).} \label{fig:hist_gwas_egene_etissue}
\end{figure*}

@@

\begin{figure*}[!tbp]

\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

\begin{subfigure}[]{.32\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{e}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{f}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

\begin{subfigure}[]{.32\textwidth}
\textbf{g}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{h}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{i}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/missense_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/splice_region_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/3_prime_UTR_variant.png}
%
\end{subfigure}
%
\caption{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: \textbf{a}, Missense variant, \textbf{b}, splice region variant and \textbf{c}, 3' UTR variant.} \label{fig:vep_consequence}
%
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{Count of egenes per variant-tissue (\textbf{a}), etissues per variant-egene (\textbf{b}) and GWAS categories per variant-egene-etissue (\textbf{c}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remaptf.py/bxplt_remaptf_per_rsid_flank_0.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_remap_crm_gwas_categories.py/remap_crm_fisher.png}
\end{subfigure}
%
\caption{Analysis of transcription factor binding. \textbf{a}, Binding count of transcription factors in the region surrounding pleiotropic variants (Radius 50 bp) as a function of the GWAS category count. \textbf{b}, Odds ratio of cis regulatory module-annotated vs non-annotated variants.} \label{fig:freq_tf_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_beta.py/eqtl_beta.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_beta.py/gwas_beta.png}
\end{subfigure}

@@

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{\textwidth}
